---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
---
<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

BioMonTools_SupportFiles 0.0.1.9011
===========
Released - 2022-12-14

* tests: Update tests for PacNW data for taxa names

BioMonTools_SupportFiles 0.0.1.9010
===========
Released - 2022-12-14

* update: Revise pick_files for PacNW (MTTI) col_drop

BioMonTools_SupportFiles 0.0.1.9009
===========
Released - 2022-12-14

* update: Revise pick_files to allow for translate and attributes files as two
separate files
* update: Revise ORWA file names and add attributes file


BioMonTools_SupportFiles 0.0.1.9008
===========
Released - 2022-12-13

* update: Revise ORWA metadata file
* udpate: Revise pick_files for revised metadata file

BioMonTools_SupportFiles 0.0.1.9007
===========
Released - 2022-12-13

* update: Revised ORWA files

BioMonTools_SupportFiles 0.0.1.9006
===========
Released - 2022-12-13

* tests: Add tests for each official taxa file to ensure taxa id official are
included in the taxa id match

BioMonTools_SupportFiles 0.0.1.9005
===========
Released - 2022-12-13

* refactor: Update picklist file to include columns to drop for projects using
the same official taxa list

BioMonTools_SupportFiles 0.0.1.9004
===========
Released - 2022-12-08

* refactor: Update picklist file to sort projects

BioMonTools_SupportFiles 0.0.1.9003
===========
Released - 2022-12-08

* refactor: Update picklist file to combine Project and Calc_Type

BioMonTools_SupportFiles 0.0.1.9002
===========
Released - 2022-12-01

* refactor: Clone to PC
* feature: Add taxa_official files
* docs: Add DESCRIPTION
* docs: Add NEWS

BioMonTools_SupportFiles 0.0.1.9001
===========
Released - 2022-12-01

* Create repository