---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
---
<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

BioMonTools_SupportFiles 0.0.1.9032
===========
Released - 2023-06-02

* feature: Add BSTI to official taxa list

BioMonTools_SupportFiles 0.0.1.9031
===========
Released - 2023-05-09

* refactor: Update pick list language 
    + Change 'Pacific Northwest' to 'Oregon/Washington'

BioMonTools_SupportFiles 0.0.1.9030
===========
Released - 2023-05-09

* refactor: Update taxa for new data
* tests: Partial update to tests to remove 'DNI' for mismatches

BioMonTools_SupportFiles 0.0.1.9029
===========
Released - 2023-02-28

* refactor: Update taxa and attributes lists for mismatches

BioMonTools_SupportFiles 0.0.1.9028
===========
Released - 2023-02-07

* fix: Update Fuzzy Thermal Ratings file

BioMonTools_SupportFiles 0.0.1.9027
===========
Released - 2023-02-07

* refactor: Add Fuzzy Thermal Ratings file

BioMonTools_SupportFiles 0.0.1.9026
===========
Released - 2023-02-03

* refactor: Remove MBSS from Index Class file

BioMonTools_SupportFiles 0.0.1.9025
===========
Released - 2023-02-01

* refactor: Update ORWA attributes BCG_Attr blanks to NA

BioMonTools_SupportFiles 0.0.1.9024
===========
Released - 2023-01-27

* refactor: Change project names in _pick_files.xlsx for taxa translate

BioMonTools_SupportFiles 0.0.1.9023
===========
Released - 2023-01-27

* refactor: Update project names in _pick_files.xlsx for taxa translate
    * OTU then project in parentheses
    * Remove non-Pacific NW references

BioMonTools_SupportFiles 0.0.1.9022
===========
Released - 2023-01-24

* refactor: Update PacNW index class required field names
    + slope_nhd to pslope_nhd

BioMonTools_SupportFiles 0.0.1.9021
===========
Released - 2023-01-23

* refactor: Update PacNW index class required field names
    + GRADIENT to slope_nhd
    + ELEVATION to elev_m

BioMonTools_SupportFiles 0.0.1.9020
===========
Released - 2023-01-12

* refactor: Update PacNW files and picklist file

BioMonTools_SupportFiles 0.0.1.9019
===========
Released - 2023-01-06

* refactor: Add test taxa lists for PacNW
* tests: Update tests for taxa lists
* feature: Add Index_Class.xlsx for use with assign_IndexClass function

BioMonTools_SupportFiles 0.0.1.9018
===========
Released - 2022-12-23

* refactor: Update file names
* docs: Update .gitignore

BioMonTools_SupportFiles 0.0.1.9017
===========
Released - 2022-12-20

* tests: Update tests for duplicates in main taxaid field

BioMonTools_SupportFiles 0.0.1.9016
===========
Released - 2022-12-20

* refactor: pick_files.csv taxaid_drop NA to NULL to match function default

BioMonTools_SupportFiles 0.0.1.9015
===========
Released - 2022-12-20

* fix: Update PacNW OR WA data
* refactor: Update pickfiles with taxaid_drop
    + Name for taxa to drop from analyses.  Only 1 name allowed, e.g., 'DNI'

BioMonTools_SupportFiles 0.0.1.9014
===========
Released - 2022-12-16

* tests: Add test for duplicate names
* fix: Remove duplicates in OR_WA master taxa file

BioMonTools_SupportFiles 0.0.1.9013
===========
Released - 2022-12-14

* feature: Add "archive" folder for historical reference of taxa translator 
files

BioMonTools_SupportFiles 0.0.1.9012
===========
Released - 2022-12-14

* update: Update PacNW "Bob" to "Biodiversity Index"

BioMonTools_SupportFiles 0.0.1.9011
===========
Released - 2022-12-14

* tests: Update tests for PacNW data for taxa names

BioMonTools_SupportFiles 0.0.1.9010
===========
Released - 2022-12-14

* update: Revise pick_files for PacNW (MTTI) col_drop

BioMonTools_SupportFiles 0.0.1.9009
===========
Released - 2022-12-14

* update: Revise pick_files to allow for translate and attributes files as two
separate files
* update: Revise ORWA file names and add attributes file


BioMonTools_SupportFiles 0.0.1.9008
===========
Released - 2022-12-13

* update: Revise ORWA metadata file
* udpate: Revise pick_files for revised metadata file

BioMonTools_SupportFiles 0.0.1.9007
===========
Released - 2022-12-13

* update: Revised ORWA files

BioMonTools_SupportFiles 0.0.1.9006
===========
Released - 2022-12-13

* tests: Add tests for each official taxa file to ensure taxa id official are
included in the taxa id match

BioMonTools_SupportFiles 0.0.1.9005
===========
Released - 2022-12-13

* refactor: Update picklist file to include columns to drop for projects using
the same official taxa list

BioMonTools_SupportFiles 0.0.1.9004
===========
Released - 2022-12-08

* refactor: Update picklist file to sort projects

BioMonTools_SupportFiles 0.0.1.9003
===========
Released - 2022-12-08

* refactor: Update picklist file to combine Project and Calc_Type

BioMonTools_SupportFiles 0.0.1.9002
===========
Released - 2022-12-01

* refactor: Clone to PC
* feature: Add taxa_official files
* docs: Add DESCRIPTION
* docs: Add NEWS

BioMonTools_SupportFiles 0.0.1.9001
===========
Released - 2022-12-01

* Create repository